### 2021-05-27 LaTeX-ACM/sections/paper.tex
some edits

The most similar academic work to this paper is the Ethereum-based periodic auction by Galal \etal~\cite{galalpublicly} and the continuous-time exchange TEX~\cite{khalil2019tex}. As with us, front-running is a main consideration of these works. In a recent SoK on front-running attacks in blockchain~\cite{eskandari2019sok}, three general mitigations are proposed. Both of these papers use the solution of providing confidentiality over the content of orders. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second mitigation approach is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third-party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach with \cm which uses \textit{no cryptography} and is \textit{submit-and-go} for traders. A detailed comparison of front-running is provided in Section~\ref{sec:front}.

@@

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like Galal \etal~\cite{}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).

\subsection{Cleaning Up Revisited}

>>>>

The most similar academic work to this paper is the Ethereum-based periodic auction by Galal \etal~\cite{galalpublicly} and the continuous-time exchange TEX~\cite{khalil2019tex}. As with us, front-running is a main consideration of these works. In a recent SoK on front-running attacks in blockchain~\cite{eskandari2019sok}, three general mitigations are proposed. Both of these papers use the solution of providing confidentiality over the content of orders. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second mitigation approach is to sequence transactions according to some rule, either at the protocol level~\cite{kelkar2020order} or as a third-party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach with \cm which uses \textit{no cryptography} and is \textit{submit-and-go} for traders. A detailed comparison of front-running is provided in Section~\ref{sec:front}.

@@

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like \textblue{Galal \etal~\cite{galal2018verifiable}}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).

\textblue{\subsection{Cleaning Up Revisited}}
